A Guide to Designing Experiments to Test Statistical Graphics

### 2022-07-05 index.qmd
Tightening language

In our experience, one of the most difficult components of designing an experiment which asks users to directly estimate information from a chart using a full scenario (background information, etc. as well as contextual details from the chart) is that the selection and wording of such questions must be extremely carefully determined.
Mathematics education researchers have provided guidelines for selecting different levels of questioning in order to assess graph comprehension: literal reading of the data, reading between the data, and reading beyond the data \cite{wood1968objectives, curcio1987comprehension, friel2001making, glazer2011challenges}. In a recent study, we identified questions based on this framework for evaluating direct estimates and extending those estimates to make comparisons between two points.

>>>>

One of the most difficult components of designing an experiment which asks users to directly estimate information from a chart using a full scenario (background information, etc. as well as contextual details from the chart) is that the questions must be extremely carefully constructed.
Mathematics education researchers provide guidelines for selecting different levels of questioning in order to assess graph comprehension: literal reading of the data, reading between the data, and reading beyond the data \cite{wood1968objectives, curcio1987comprehension, friel2001making, glazer2011challenges}. In a recent study, we identified questions based on this framework to evaluate direct estimates and extend those estimates to make comparisons between two points.
